---
title: "DataAnalysis - Postprocessing Results MaxQuant"
autor: David Lilek
date: "`r format(Sys.time(), '%d %B %Y, %X')`"
output:
  html_document:
    df_print: paged
    fig.align: center
    self_contained: yes
    fig.height: 4
    fig.width: 8
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
    code_folding: hide
---

```{r start, message=FALSE, warning=FALSE, include=FALSE}
start_time = format(Sys.time(), '%X')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
#load libraries
library(tidyverse)
library(dplyr)
library(gplots)
library(reshape2) #for melting data for boxplot with ggplot
library(pheatmap)
```

# Introduction

## LFQ-Procedure

Filtering:

-   `Potential.contaminant == ""` -> remove where contaminants
-   `Reverse == ""`-> remove where reverse = +
-   `Only.identified.by.site == ""` -> remove where only identified by site = +

Then the `log2`of the LFQ intensities was calculated and all `-Inf` values were substituted by NA using the following command: `lfq[lfq == -Inf] <- NA`

Then the number of lfq values was used for the further evaluation, visualization and statistical testing. In the following this data will be called LFQ.

## Unique | Razor&Unique procedure

Filtering:

-   `Potential.contaminant == ""` -> remove where contaminants
-   `Reverse == ""`-> remove where reverse = +
-   `Only.identified.by.site == ""` -> remove where only identified by site = +

-   `data[name] >= unique` -> keep only identifications which have greater or equal number (defined via variable `unique`) of `razor/unique peptides ` | in this case `unique`was set to 2.

# Data Analysis

The txt-files were read in, processed and filtered automatically. This section shows the code, several plots and also some summary statistics which are only shown for further discussion on the results, for the documentation of the statistical evaluation and are not labeled/discussed yet. If you are interested in the summary of the results go to `Summary`.

```{r, results="asis"}
###############################
#
#define settings
#
###############################

GET_SAMPLE_NAMES <- TRUE # if set to false define it in the next line
# sample_names_raw <- c("A1","A2","A3")
unique <- 2  #how many peptides should be necessary to identify a protein

RAZOR <- TRUE #TRUE | FALSE
UNIQUE <- TRUE #TRUE | FALSE
LFQ <- TRUE #TRUE | FALSE

path = "N:/1_A_Bachelor_Master_Intern/00_M_2022/David/Data/3_20220406_TR/20220406_TR_QC_noMBR_pooled_rerun_4masterthesis/"
#path = "N:/1_A_Bachelor_Master_Intern/00_M_2022/David/R/"

# load functions
filtering <- function(data_raw){
  data_raw %>% filter( 
    Potential.contaminant == "",
    Reverse == "",
    Only.identified.by.site == "")
}

CV <- function(x){
  (sd(x)/mean(x))*100
}

##########read in all data with pattern .txt
# get file list
file.list <- list.files(path = path, pattern='*.txt')
# create file path
file.path <- paste(path,file.list,sep = "")
# read in files - for each file one variable is created - results are stored in a list
res_raw <- lapply(file.path, read.delim)
names(res_raw) <- file.list

#get sample names
if (GET_SAMPLE_NAMES == TRUE){
    tmp <- colnames(res_raw[[1]])
    tmp <- tmp[grep("Razor...unique.peptides.",tmp)]
    tmp <- sub(".*Razor...unique.peptides.", "",tmp)
    sample_names_raw <- tmp
    rm(tmp)
}

sample_names_razor <- paste("Razor...unique.peptides.",sample_names_raw, sep="")
sample_names_unique <- paste("Unique.peptides.",sample_names_raw, sep="")
sample_names_lfq <- paste("LFQ.intensity.",sample_names_raw, sep="")
#another option would be
#uniq <- data %>% select(starts_with("Unique.peptides."))

#create data frame for razor
results_2gether_razor <- data.frame(matrix(ncol = length(sample_names_raw), nrow = length(file.list)))
row.names(results_2gether_razor) <- file.list
colnames(results_2gether_razor) <- sample_names_raw
#create data frame for unique
results_2gether_unique <- data.frame(matrix(ncol = length(sample_names_raw), nrow = length(file.list)))
row.names(results_2gether_unique) <- file.list
colnames(results_2gether_unique) <- sample_names_raw
#create data frame for lfq
results_2gether_lfq <- data.frame(matrix(ncol = length(sample_names_raw), nrow = length(file.list)))
row.names(results_2gether_lfq) <- file.list
colnames(results_2gether_lfq) <- sample_names_raw


#results lists
results_razor <- list()
results_unique <- list()
results_lfq <- list()

if (RAZOR == TRUE) {
  cat("\n")
  cat("##","Razor","\n")
  cat("\n")
for (x in file.list){
  cat("\n")
  cat("###",substring(x, 1, nchar(x)-4),"\n")
  data_raw <- as.data.frame(res_raw[[x]])
  data <- filtering(data_raw)
  results <- data.frame(matrix(ncol = length(sample_names_raw), nrow = nrow(data)))
  colnames(results) <- sample_names_raw
  i <- 0
  for (i in 1:length(sample_names_razor)){
    name <- sample_names_razor[i]
    tmp <- (data[name] >= unique)
    results[i] <- tmp
    cat(name,"<br/>",sum(tmp, na.rm = TRUE),"<br/>")
  }
  
  results_razor[[x]] <- results
  #assign(paste("results_razor",x,sep="_"),results) #create individual variable names
  
  #make venn diagramm
  #venn(results)
  
  results_2gether_razor[x,] <- sapply(results,function(x)sum(x, na.rm = TRUE))
  cat("\n")
}
}

if (UNIQUE == TRUE) {
  cat("\n")
  cat("##","Unique","\n")
  cat("\n")
for (x in file.list){
  cat("\n")
  cat("###",substring(x, 1, nchar(x)-4),"\n")
  data_raw <- as.data.frame(res_raw[[x]])
  data <- filtering(data_raw)
  results <- data.frame(matrix(ncol = length(sample_names_raw), nrow = nrow(data)))
  colnames(results) <- sample_names_raw
  i <- 0
  for (i in 1:length(sample_names_unique)){
    name <- sample_names_unique[i]
    tmp <- (data[name] >= unique)
    results[i] <- tmp
    cat(name,"<br/>",sum(tmp, na.rm = TRUE),"<br/>")
  }
  
  results_unique[[x]] <- results
  #assign(paste("results_razor",x,sep="_"),results) #create individual variable names
  
  #make venn diagramm
  #venn(results)
  
  results_2gether_unique[x,] <- sapply(results,function(x)sum(x, na.rm = TRUE))
  cat("\n")
}
}

if (LFQ == TRUE) {
    cat("\n")
  cat("##","LFQ","\n")
  cat("\n")
  for (x in file.list){
    cat("\n")
    cat("###",substring(x, 1, nchar(x)-4),"\n")
    data_raw <- as.data.frame(res_raw[[x]])
    data <- filtering(data_raw)
    
    results <- data.frame(matrix(ncol = length(sample_names_raw), nrow = nrow(data)))
    colnames(results) <- sample_names_raw
    i <- 0
    for (i in 1:length(sample_names_lfq)){
      name <- sample_names_lfq[i]
      tmp <- log2(data[name])
      tmp[tmp == -Inf] <- NA
      results[i] <- tmp
      cat(name,"<br/>",sum(!is.na(tmp)),"<br/>")
      
    }
    
    results_lfq[[x]] <- results
    #assign(paste("results_lfq",x,sep="_"),results) #create individual variable names
    


    
    results_2gether_lfq[x,] <-    sapply(results,function(x)sum(!is.na(x)))
    cat("\n")
    
  }
}

#add number in column 4 for selection
results_2gether_razor$number <- c(1:length(file.list))
results_2gether_unique$number <- c(1:length(file.list))
results_2gether_lfq$number <- c(1:length(file.list))

#remove variables - clean up
rm(data,
   data_raw,
   name,
   results,
   sample_names_razor,
   sample_names_unique,
   sample_names_lfq,
   tmp,
   x)
```

# Used time

```{r end, message=FALSE, warning=FALSE, include=FALSE}
end_time = format(Sys.time(), '%X')
```

```{r}
res <- data.frame(cbind(results_2gether_razor$QC,results_2gether_unique$QC,results_2gether_lfq$QC))
colnames(res) <- c("Razor", "Unique", "LFQ")
write.csv2(res, file = "./tmpfiles/20220406_TR_QC_noMBR_pooled_rerun.csv")
```

